% arara: xelatex
% arara: xelatex
% arara: xelatex

% options:
% thesis=B bachelor's thesis
% thesis=M master's thesis
% czech thesis in Czech language
% english thesis in English language
% hidelinks remove colour boxes around hyperlinks

\documentclass[thesis=M,english]{prefs/FITthesis}[2019/03/06]

% \usepackage{subfig} %subfigures
% \usepackage{amsmath} %advanced maths
% \usepackage{amssymb} %additional math symbols

\usepackage[utf8]{inputenc}

\usepackage{graphicx} %graphics files inclusion
% \usepackage{amsmath} %advanced maths
% \usepackage{amssymb} %additional math symbols

\usepackage{dirtree} %directory tree visualisation
\usepackage{subfig} %image side by side
\usepackage{todonotes} %todo
\usepackage{url}
\usepackage{textcomp} %degree symbol
\usepackage{color, colortbl} %color, table color
\usepackage{enumitem} %lists
\usepackage{float} %for H option in figures
\usepackage{array} %table aligment       
\usepackage{amsmath} %cases
\usepackage{amssymb}
\usepackage{svg} %svg
\usepackage{scrextend}
\usepackage{multirow}
\addtokomafont{labelinglabel}{\sffamily}

\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{Blue}{rgb}{0.30980, 0.50588, 0.73725}
\definecolor{White}{rgb}{1, 1, 1}

% list of acronyms
\usepackage[acronym,nonumberlist,toc,nopostdot,numberedsection=autolabel,nomain]{glossaries}
\makeglossaries
\newcommand{\tg}{\mathop{\mathrm{tg}}} %cesky tangens
\newcommand{\cotg}{\mathop{\mathrm{cotg}}} %cesky cotangens

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\department{Department of Applied Mathematics}
\title{People detection, tracking and biometric data extraction using a single camera for retail usage}
\authorGN{Luk{\' a}{\v s}} %author's given name/names
\authorFN{Brchl} %author's surname
\authorWithDegrees{Bc. Luk{\' a}{\v s} Brchl} %author's name with academic degrees
\author{Luk{\' a}{\v s} Brchl} %author's name without academic degrees
\supervisor{doc. RNDr. Ing. Marcel Jiřina, Ph.D.}
\acknowledgements{First of all, I would like to thank my supervisor Assoc. Prof. Marcel Jiřina who gave rise to this assignment but also hired me to ImproLab, which was a unique opportunity to gain new professional knowledge. I have already spent more than two great years in this group doing work I enjoyed. This opportunity has dramatically shifted my thinking further.

I also thank all my colleagues from ImproLab for creating a pleasant everyday working environment. Our regular team-building events had extremely positive repercussions on my work. Specifically thanks to Ing. Jakub Novák for proofreading.

I want to express my gratitude to my co-supervisor Prof. Kai-Lung Hua from Taiwan Tech, thanks to which I was able to work on this thesis in such a beautiful country like Taiwan. I am also grateful for his course Deep Learning for Computer Vision Applications where I could revive my current knowledge of this field. The stay in Taiwan has been a fantastic experience, beneficial for my learning and my personal growth. I am also entirely determined to return to this lovely country in the future because of the kind and helpful people that can be found here.

Many thanks to the wonderful research community that exists in machine learning and computer vision field. Without so many materials, frameworks, libraries, and open-source models, this work could not arise.

I would also like to thank my family because, despite the challenging situations I faced during the studies, they have always supported my ideas and choices and provided me with lots of love.

Last but not least, big thanks to my girlfriend Michaela, who has been tirelessly supporting me throughout the last four years and also making sure that I do not run out of food during the writing of this work.
}
\abstractCS{Tato práce se zabývá návrhem frameworku, který slouží k analýze video sekvencí z RGB kamery. Framework využívá technik sledování osob a následné extrakce biometrických dat. Biometrická data jsou sbírána za účelem využití v malobochodním prostředí. Navržený framework lze rozdělit do třech menších komponent, tj. detektor osob, sledovač osob a extraktor biometrických dat. Navržený detektor osob využívá různé architektury sítí hlubokého učení k určení polohy osob. Řešení pro sledování osob se řídí známým postupem \uv{online tracking-by-detection} a je navrženo tak, aby bylo robustní vůči zalidněným scénám. Toho je dosaženo začleněním dvou metrik týkající se vzhledu a stavu objektu v asociační fázi. Kromě výpočtu těchto deskriptorů, jsme schopni získat další informace o jednotlivcích jako je věk, pohlaví, emoce, výška a trajektorie. Návržené řešení je ověřeno na datasetu, který je vytvořen speciálně pro tuto úlohu.}
\abstractEN{This thesis proposes a framework that analyzes video sequences from a single RGB camera by extracting useful soft-biometric data about tracked people. The aim is to focus on data that could be utilized in a retail environment. The designed framework can be broken down into the smaller components, i.e., people detector, people tracker, and soft-biometrics extractor. The people detector employs various deep learning architectures that estimate bounding boxes of individuals. The tracking solution follows the well-known online tracking-by-detection approach, while the proposed solution is built to be robust regarding the crowded scenes by incorporating appearance and state features in the matching phase. Apart from calculating appearance descriptors only for matching, we extract additional information of each person in the form of age, gender, emotion, height, and trajectory when possible. The whole framework is validated against the dataset which was created for this propose.}
\placeForDeclarationOfAuthenticity{Prague} %where you have signed the declaration
\keywordsCS{počítačové vidění, detekce osob, sledování osob, extrakce biometrických údajů\newpage}
\keywordsEN{computer vision, people detection, people tracking, biometrics extraction}
\declarationOfAuthenticityOption{5} %select as appropriate, according to the desired license
\website{https://github.com/lukasbrchl/People-detection-tracking-and-biometrics-extraction-using-a-single-camera-text} %optional URL (remove entirely if you have no URL for this thesis)

\newacronym{ann}{ANN}{artificial neural network}
\newacronym{ai}{AI}{artificial intelligence}
\newacronym{cmos}{CMOS}{complementary metal oxide semiconductor}
\newacronym{cnn}{CNN}{convolutional neural network}
\newacronym{ctu}{CTU}{Czech Technical University}
\newacronym{cpu}{CPU}{central processing unit}
\newacronym{cv}{CV}{computer vision}
\newacronym{dex}{DEX}{Deep EXpectation}
\newacronym{dl}{DL}{deep learning}
\newacronym{dlt}{DLT}{Direct Linear Transform}
\newacronym{dsae}{DSAE}{deep sparse autoencoders}
\newacronym{fast r-cnn}{Fast R-CNN}{fast region-based convolutional network}
\newacronym{faster r-cnn}{Faster R-CNN}{faster region-based convolutional network}
\newacronym{fce}{FCE}{Faculty of Civil Engineering}
\newacronym{fit}{FIT}{Faculty of Information Technology}
\newacronym{fn}{FN}{false negatives}
\newacronym{fp}{FP}{false positives}
\newacronym{fps}{FPS}{frames per second}
\newacronym{gige}{GigE}{Gigabit Ethernet}
\newacronym{gpu}{GPU}{graphics processing unit}
\newacronym{hog}{HOG}{histogram of oriented gradients}
\newacronym{hsv}{HSV}{hue-saturation-value}
\newacronym{idsw}{IDSW}{identity switches}
\newacronym{improlab}{ImproLab}{Image Processing Laboratory}
\newacronym{iou}{IoU}{intersection over union}
\newacronym{lbp}{LBP}{local binary pattern}
\newacronym{lstm}{LSTM}{long short-term memory}
\newacronym{mae}{MAE}{mean absolute error}
\newacronym{ml}{ML}{machine learning}
\newacronym{mlp}{MLP}{multi layer perceptron}
\newacronym{mot}{MOT}{multiple object tracking}
\newacronym{mota}{MOTA}{multiple object tracking accuracy}
\newacronym{motp}{MOTP}{multiple object tracking precision}
\newacronym{mots}{MOTS}{multiple object tracking and segmentation}
\newacronym{mp}{MP}{megapixel}
\newacronym{mtmct}{MTMCT}{multi-target multi-camera tracking}
\newacronym{nms}{NMS}{non-maximum suppression}
\newacronym{nn}{NN}{neural network}
\newacronym{pca}{PCA}{principal component analysis}
\newacronym{r-cnn}{R-CNN}{region-based convolutional network}
\newacronym{reid}{ReID}{re-identification}
\newacronym{rgb}{RGB}{red-green-blue}
\newacronym{roi}{RoI}{region of interest}
\newacronym{rmse}{RMSE}{root-mean-square error}
\newacronym{rnn}{RNN}{recurrent neural network}
\newacronym{rpn}{RPN}{region proposal network}
\newacronym{sdk}{SDK}{software development kit}
\newacronym{sift}{SIFT}{Scale-invariant feature transform}
\newacronym{sort}{SORT}{simple online and real-time tracking}
\newacronym{ssd}{SSD}{single-shot detector}
\newacronym{ssr}{SSR-Net}{Soft Stagewise Regression Network}
\newacronym{surf}{SURF}{Speeded-Up Robust Features}
\newacronym{spp}{SPP}{spatial pyramid pooling}
\newacronym{svm}{SVM}{support vector machine}
\newacronym{yolo}{YOLO}{you only look once}


\begin{document}
    \input{src_text/00_introduction.tex}
    \input{src_text/01_theoretical_background.tex}
    \input{src_text/02_related_work.tex}
    \input{src_text/03_methodology.tex}
    \input{src_text/04_implementation.tex}
    \input{src_text/05_evaluation.tex}
    \input{src_text/06_conclusion.tex}
    
    % bibliography
    \bibliographystyle{prefs/iso690}
    \bibliography{ref}
    
    \appendix
    
    % acronyms
    \printglossaries
    
    % media contents
    \chapter{Media contents}\label{app:CDcontent}
    \begin{figure}
    	\dirtree{%
    		.1 readme.txt\DTcomment{the file with CD contents description}.
    		.1 data\DTcomment{the data files directory}.
    		.2 example\textunderscore sequence\DTcomment{the directory with example sequence from dataset}.
    		.3 *.jpg\DTcomment{the example images}.
    		.2 example\textunderscore sequence\textunderscore graphs\DTcomment{the directory of graphs of experiments}.
    		.3 *.png\DTcomment{the motion output graphs}.
    		.2 tracking\textunderscore example.mp4\DTcomment{the example video file}.
    		.1 src\DTcomment{the directory of source codes}.
    		.2 models\DTcomment{the directory of deep learning modules}.
    		.2 utils\DTcomment{the directory of helper modules}.
    		.2 *.py\DTcomment{the Python source files}.
    		.1 text\DTcomment{the thesis text directory}.
    		.2 thesis\DTcomment{the directory of \LaTeX{} source codes of the thesis}.
    		.2 thesis.pdf\DTcomment{the Diploma thesis in PDF format}.
    	}
    \end{figure}
    

\end{document}
